\documentclass[12pt]{report}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}

\begin{document}

\begin{titlepage}
\centering

{\color{blue}\Huge \textbf{AKSHAR AI LTD}}\\[0.8cm] 

{\color{blue}\rule{12cm}{1pt}}\\[1.2cm]

{\Huge \textbf{AI/ML Model Performance}}\\[0.2cm]
{\Huge \textbf{Benchmarking Tracker}}\\[1cm]

{\color{blue}\rule{10cm}{1pt}}\\[1cm]

{\Large \color{red}\textbf{Internship Project Report}}\\[2cm]

\begin{flushleft}

\textbf{Prepared By:} Shanvi Sinha\\[0.5cm]

\textbf{Enrollment No:} 24162581051\\[0.5cm]

\textbf{Branch:} Computer Science and Engineering\\[0.5cm]

\textbf{University:} Ganpat University\\[0.5cm]

\textbf{Mentor:} Lokesh Budhia\\[0.5cm]

\textbf{Company:} Akshar AI LTD\\[0.5cm]

\textbf{Date:} \\[0.5cm]

\textbf{Status:} 

\end{flushleft}

\vfill

\end{titlepage}



\tableofcontents
\newpage

\setcounter{chapter}{0}

\chapter{Introduction}

Artificial Intelligence (AI) and Machine Learning (ML) are rapidly transforming the way organizations and individuals solve problems using data. Machine learning models are widely used in various fields such as healthcare, finance, recommendation systems, image recognition and natural language processing. As the number of available machine learning algorithms continues to increase selecting the most suitable model for a specific task becomes challenging.

\par\vspace{0.5cm}

Different machine learning models often produce different results when applied to the same dataset. Therefore, evaluating and comparing model performance is essential to ensure accurate and reliable outcomes. Important metrics such as Accuracy, Precision, Recall, F1-Score and Execution Time are commonly used to measure model effectiveness.

\par\vspace{0.5cm}

The AI/ML Model Performance Benchmarking Tracker is designed to address this challenge by providing a structured framework for evaluating, comparing and monitoring machine learning models. The project records key performance metrics and presents them in an organized manner, enabling users to identify the strengths and weaknesses of different models. By simplifying the model evaluation process the benchmarking tracker helps students, researchers and developers make informed decisions and select the most appropriate machine learning model for their specific requirements.

\chapter{Problem Statement}


In today's world, many machine learning models are available for solving similar problems. However, selecting the most suitable model can be difficult because each model performs differently depending on the dataset and application. Students, researchers, and developers often spend considerable time testing multiple models and comparing their results manually.

\par\vspace{0.5cm}

Without a proper system tracking model performance becomes challenging and time-consuming. Important evaluation metrics such as Accuracy, Precision, Recall, F1-Score and Execution Time may be stored in different places making comparison difficult and sometimes inaccurate.

\par\vspace{0.5cm}

The AI/ML Model Performance Benchmarking Tracker aims to solve this problem by providing a centralized platform for evaluating, recording, and comparing machine learning model performance. The system helps users analyze results efficiently and select the most appropriate model based on objective performance metrics.

\end{document}
